Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
commenting out ggpairs

```{r load packages, include=TRUE}
#adding this line as a git test
#install specific versions of pakages called out in the paper
#require(devtools)
library(devtools)

#install_version("geomorph", version = "3.0.6", repos = "http://cran.us.r-project.org")
#install.packages("http://https://cran.r-project.org/src/contrib/Archive/geomorph/geomorph_3.0.6.tar.gz", repos=NULL, type="source")
library(geomorph) # geomorph 3.0.6

@@

ggpairs(lances_M, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8v1.png"))

@@

```{r replication corr test, include=TRUE, echo=FALSE}
ggpairs(lances_M[complete.cases(lances_M),], columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_complete_cases_manual.png"))

ggpairs(blade, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_blade.png"))

ggpairs(socket, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_socket.png"))

ggpairs(total, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_blades_and_sockets.png"))
```

>>>>

## Methods

## Results

##

```{r load packages, include=TRUE}
#adding this line as a git test
#install specific versions of pakages called out in the paper
#require(devtools)
library(devtools)
#install_version("geomorph", version = "3.0.6", repos = "http://cran.rstudio.com")
#install_version("geomorph", version = "3.0.6", repos = "http://cran.r-project.org")
#install.packages("http://https://cran.r-project.org/src/contrib/Archive/geomorph/geomorph_3.0.6.tar.gz", repos=NULL, type="source")
library(geomorph) # geomorph 3.0.6

@@

#COMMENTED OUT BY THOMAS IN ORDER TO KNIT
#ggpairs(lances_M, columns = c("total_length", "blade_length", "socket_length", #"sock_bdiam", "sock_sdiam", "width", "thickness"), 
#        upper=list(continuous = upper_fn),
#        diag=list(continuous = diag_fn),
#        lower=list(continuous = "cor")) + theme_minimal() +
#        ggsave(here("Images","replication_fig_8v1.png"))

ggpairs(lances_M, columns = c('total_length', 'blade_length', 'socket_length', 'sock_bdiam', 'sock_sdiam', 'width', 'thickness'),  
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8v1.png"))

@@

```{r replication corr test 2, include=TRUE, echo=FALSE}
#COMMENTED OUT BY THOMAS IN ORDER TO KNIT
#ggpairs(lances_M[complete.cases(lances_M),], columns = c("total_length", "blade_length", #"socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
#        upper=list(continuous = upper_fn),
#        diag=list(continuous = diag_fn),
#        lower=list(continuous = "cor")) + theme_minimal() +
#        ggsave(here("Images","replication_fig_8_complete_cases_manual.png"))

#COMMENTED OUT BY THOMAS IN ORDER TO KNIT
#ggpairs(blade, columns = c("total_length", "blade_length", "socket_length", #"sock_bdiam", "sock_sdiam", "width", "thickness"), 
#        upper=list(continuous = upper_fn),
#        diag=list(continuous = diag_fn),
#        lower=list(continuous = "cor")) + theme_minimal() +
#        ggsave(here("Images","replication_fig_8_blade.png"))

#COMMENTED OUT BY THOMAS IN ORDER TO KNIT
#ggpairs(socket, columns = c("total_length", "blade_length", "socket_length", #"sock_bdiam", "sock_sdiam", "width", "thickness"), 
#        upper=list(continuous = upper_fn),
#        diag=list(continuous = diag_fn),
#        lower=list(continuous = "cor")) + theme_minimal() +
#        ggsave(here("Images","replication_fig_8_socket.png"))

#COMMENTED OUT BY THOMAS IN ORDER TO KNIT
#ggpairs(total, columns = c("total_length", "blade_length", "socket_length", #"sock_bdiam", "sock_sdiam", "width", "thickness"), 
#        upper=list(continuous = upper_fn),
#        diag=list(continuous = diag_fn),
#        lower=list(continuous = "cor")) + theme_minimal() +
#        ggsave(here("Images","replication_fig_8_blades_and_sockets.png"))
```
